---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HW3

<!-- badges: start -->
[![R-CMD-check](https://github.com/Kumachar/BIOSTAT625HW3B/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Kumachar/BIOSTAT625HW3B/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Kumachar/BIOSTAT625HW3B/branch/master/graph/badge.svg)](https://app.codecov.io/gh/Kumachar/BIOSTAT625HW3B?branch=master)
<!-- badges: end -->

The goal of this package HW3 is to facilitate get linear regression result and its analysis. It includes functions for building linear models, making predictions, testing parameters, and summarizing model results.

## Installation

You can install the newest version of HW3 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Kumachar/BIOSTAT625HW3B")
```
## Function List

1. **linear_model(X, y, intercept = TRUE)**: Builds a linear model. 
    - `X`: Predictor variables (matrix or data frame). 
    - `y`: Response variable (matrix or data frame).
    - `intercept`: Whether to include the intercept (default: TRUE). 
    - Returns a list with model coefficients, fitted values, residuals, rank, mean squared error, model data, intercept inclusion status, and NA removal details.
    
2. **parameter_t_test(model)**: Conducts t-tests and F-tests on model parameters. -->
    - `model`: The linear model object returned by `linear_model`. 
    - Returns a list with estimates, standard errors, t-values, p-values for t-tests, F-value, p-value for F-test, R², and adjusted R². 

 3. **linear_prediction(X, b, intercept = TRUE)**: Generates predictions using the linear model.
    - `X`: Predictor variables (matrix or data frame). 
    - `b`: Coefficients of the linear model. 
    - `intercept`: Whether the intercept was included in the model.
    - Returns predicted values. 

 4. **Linear_regression(X, y, intercept = TRUE)**: Helper function for `linear_model` to perform linear regression.
    - `X`: Predictor variables (matrix or data frame). 
    - `y`: Response variable (matrix or data frame).
    - `intercept`: Whether to include the intercept.
    - Returns regression coefficients. 

 5. **model_summary(model, show_table = TRUE)**: Summarizes the linear model. 
    - `model`: The linear model object returned by `linear_model`. 
    - `show_table`: Whether to display the summary table (default: TRUE). 
    - Returns test results and optional



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(HW3)
## basic example code
```

Now we can display a simple example of how this package works. We are going to use linear model to predict the Miles per gallon based on horse power and weight of a car in mtcars data.

```{r cars}
data("mtcars")
X <- mtcars[, c("hp", "wt")]
y <- mtcars$mpg

#Construct a Multiple Linear Regression model to predict Miles per gallon based on horse power and weight of a car
model <- linear_model(X, y, intercept = TRUE)

#Now we can see the regression coefficients for each variable you use in the model
model$coefficients

#Also we can predict data based on acquired coefficients use lineaer_prediction function
head(linear_prediction(X,model$coefficients))

```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
